Project 2

### 2023-05-24 Misc/htw_dp.qmd
small changes

We developed a novel visuomotor extrapolation task, termed the ["Hit The Wall"
(HTW]{.underline}) task, wherein participants learned to launch a projectile
such that it hit a rectangle at the far end of the screen with an appropriate
amount of force. Although the projectile had both x and y velocity components,
only the x-dimension was relevant for the task.\ 
[Link to task demo](https://pcl.sitehost.iu.edu/tg/HTW/HTW_Index.html?sonaid=){target="_blank"}

@@

## Model Equations
:::{.column-page-inset-right}
```{r ALM_Table, results='asis'}

@@

# References 
<div id="refs"></div>
```{=tex}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```

>>>>

We developed a novel visuomotor extrapolation task, termed the ["Hit The Wall" (HTW]{.underline}) task, wherein participants learned to launch a projectile such that it hit a rectangle at the far end of the screen with an appropriate amount of force. Although the projectile had both x and y velocity components, only the x-dimension was relevant for the task.  [Link to task demo](https://pcl.sitehost.iu.edu/tg/HTW/HTW_Index.html?sonaid=){target="_blank"}

@@

## Model Equations

::: column-page-inset-right
```{r ALM_Table, results='asis'}

@@

# References

::: {#refs}
:::

```{=tex}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
<br><br>
